---
title: "Anomaly Detection"
author: "Waiyego Mburu"
date: "15/07/2021"
output: html_document
---
```{r}
library(tidyverse)
library(anomalize)
library(tibbletime)
library(dplyr)
```

```{r}
df3<- read.csv("http://bit.ly/CarreFourSalesDataset")
```

```{r}
head(df3)
```

```{r}
str(df3)
```

```{r}
colSums(is.na(df3))
```

```{r}
duplicates <- df3[duplicated(df3),]
duplicates
```

```{r}
# Grouping by server and converting to tibbletime

sales <- df3 %>% group_by(Date) %>%
   mutate(Date = as.Date (Date, format="%m/%d/%Y")) %>% as_tbl_time(index = Date)

head(sales)
```

```{r}
# performing anomaly detection on the sales 
sales_anomalized <- sales %>% summarise(Orders = sum(Sales)) %>%
    time_decompose(Orders) %>%
    anomalize(remainder, alpha = 0.25, max_anoms = 0.2) %>%
    time_recompose() %>%
    plot_anomalies(time_recomposed = TRUE) +
    ggtitle("alpha = 0.05, max_anoms = 0.2")
    
sales_anomalized
```

I couldn't find any anomalies with the normal Alpha of 0.05, but when I increased it to 0.25, I found some probable anomalies.

## **CONCLUSION**

* The months of February and March saw the most anomalies.
* The month of January had the fewest anomalies.

## **RECOMMENDATIONS**
* The management should check into the sales that occur in February and March because there is a risk of either losses or unexplained earnings pilfering. 
* A system that detects anomalies as soon as they occur should also be in place so that they can be explored as quickly as feasible.