---
title: "Dimensionality Reduction"
author: "Waiyego Mburu"
date: "15/07/2021"
output: html_document
---

```{r}
df<- read.csv("http://bit.ly/CarreFourDataset")
```

```{r}
head(df)
```

```{r}
str(df)
```

```{r}
colSums(is.na(df))
```

```{r}
duplicates <- df[duplicated(df),]
duplicates
```
```{r}
# check for outliers/anomalies

# Finding all columns that are numerical/not strings & subsetting to new dataframe
df_num <- df[, !sapply(df, is.character)]

par(mfrow = c(1,1), mar = c(5,4,2,2))
boxplot(df_num[, c(1,5)], main='BoxPlots')
boxplot(df_num[, c(3,6)])
boxplot(df_num[, c(2,7)])
boxplot(df_num[ ,c(4,8)])


```

We do not deal with the outliers because there are other factors that can explain them for example the seasons the purchases were made.

## IMPLEMENTING THE SOLUTION
### PCA USING R
```{r}
# creating a dataset for PCA
df1 <- df[,c(6,7,8,12,13,14,15,16)]
head(df1)
```

```{r}
# Removing the gross margin percentage column
df1 = subset(df1, select = -c(gross.margin.percentage, Total) )
```

```{r}
head(df1)
```

```{r}
pca_obj <- prcomp(df1, scale=TRUE)
summary(pca_obj)
```

After carrying out PCA, it was thereby duly noted that the first three principal components accounted for 98.71% of the total variance while the rest of the components explained very little of the variance thereby not considered.

```{r}
library(devtools)
library(ggbiplot)
```

```{r}
ggbiplot(pca_obj)
```

```{r}
ggbiplot(pca_obj, groups = as.factor(df$Branch), ellipse = TRUE, circle = TRUE)
```

```{r}
ggbiplot(pca_obj, groups = as.factor(df$Customer.type), ellipse = TRUE, circle = TRUE)
```

```{r}
ggbiplot(pca_obj, groups = as.factor(df$Product.line), ellipse = TRUE, circle = TRUE)
```

```{r}
ggbiplot(pca_obj, groups = as.factor(df$Payment), ellipse = TRUE, circle = TRUE)
```

## **CONCLUSION**
* As seen the first three principle components are the most significant since they explain **98%** of our explained variance.
* PCA wouldn't be the ideal method to use since there exists an overlap in our customers.

## **RECOMMENDATIONS**
* We should find another method of dimensionality reduction that takes into consideration the overlap. For example t-SNE.
